%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  \cventry
    {Senior Software Engineer} % Job title
    {Microsoft} % Organization
    {Dublin, Ireland} % Location
    {Oct. 2023 - Present} % Date(s)
    {}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Member of the SharePoint eSign team developing a new system to allow SharePoint premium users to create signature requests on documents.}
        \item {Worked on improving the availability, observability, reliability and performance of the services behind the eSign feature before GA.}
        \item {Lead the development of three new features requested by customers after the GA release.}
        \item {Worked alongside and eventually became the owner of an initiative to convert our service APIs into an async processing model. Prepared to launch the async creation as part of the Word integration.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Staff Software Engineer} % Job title
    {Toast} % Organization
    {Dublin, Ireland} % Location
    {Jan. 2023 - Oct. 2023} % Date(s)
    {}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Member of the International organization that is driving the international expansion of Toast.}
        \item {Lead the development of backend services used to integrated with external payment processing providers. In particular the service that handles the "host to host" integration with one of such payment providers.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Meta} % Organization
    {Dublin, Ireland - Remote} % Location
    {March. 2022 - Jan, 2023} % Date(s)
    {}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Remote member of the API Management team in London. The team is responsible for building a modern API Platform  (in PHP/Hacklang) that is compliant, privacy aware and easy to use to share data with 3rd party business.}
        \item {Re-achitected the system that generates and the external developer API documentation simplifying it by removing unnecessary dependencies and brittle batch processes. This reduced by 99\% the alerts for missing endpoint documentation from 20 a day to 1 in the last 4 months.}
        \item {Lead of the pod in charge of the systems and processes that keep the records of what data "could be" and "was" accessed by third party business. The main direction I set for team was on optimizing the current system reducing the resources utilization. We have achieved a reduction of 45\% of the CPU quota required to process the data.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Development Engineer} % Job title
    {Amazon - AWS Lambda} % Organization
    {Dublin, Ireland} % Location
    {Jun. 2020 - Oct. 2021} % Date(s)
    {}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Member of the team responsible of the languages and runtimes available in the AWS Lambda service. The Runtimes team holds responsibility for the curation, patching, and deprecation of all the managed runtimes in addition to Lambda container images.}
        \item {Designed and implemented the initial version of the Runtime Interface Clients for two of the supported runtimes (NodeJS and Python) and released them as part of the Lambda Container Interface Support.}
        \item {Led the migration of the Java8 Lambda runtime to the Corretto JVM. This involved preparing mechanisms to allow customers to test the new runtime and working directly with leadership and the product team on the migration strategy and public communication. Most of the work developed during this period has been publicly released as part of the 'Lambda Runtime Management Controls feature'.}
        \item {Led the team efforts required to enable the support of the ARM architecture in the AWS Lambda runtimes.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Software Development Engineer} % Job title
    {Amazon - AWS L7 Loadbalancing} % Organization
    {Dublin, Ireland} % Location
    {Oct. 2017 - Jun. 2020} % Date(s)
    {}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Member of the team responsible for the administrative part of the software stack used to manage the internal load balancers used globally by the whole company.}
        \item {Automated the region builds of our services removing almost all the manual operations and reducing the time taken to build our services into a new region from 2 weeks to 2 days.}
        \item {Designed and developed the integration testing tools and End to End tests for the Load balancing Control plane web tools.}
        \item {Launched the Web UI of the new Control Plane for internal Load balancing.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {United Nations Office in Vienna} % Organization
    {Vienna, Austria} % Location
    {Jan. 2013 - Sep. 2017} % Date(s)
    {}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Participated in the maintenance and development of new features for two web applications used to manage the services required for the smooth functioning of UN conferences all over the globe including the UN General Assembly.}
        \item {Developing tools to help in the translation of documents between the 6 official UN languages with suggestions from different sources including Statistical Machine Translation, Terminology databases, and similar text found on historical translated documents.}
        \item {Optimised a series of queries and implemented a smart caching of the results reducing database hits and memory footprint in the translation suggestions services achieving up to a 70\% decrease on memory allocation in one them.}
        \item {Lead the design, development and successful release of a new service called the Document Web Search Tool.}
        \item {Improved the library that handles the import/export of text allowing the application to correctly import the text from Word files and export the text translation without losing the document format.}
        \item {Implemented a new version of the document symbol recognition library used to detect appearances of UN document symbols in text, improving the detection and correct generation of links to the documents.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Grupo Advantage} % Organization
    {Cd. de Mexico, Mexico} % Location
    {Mar. 2011 - Aug. 2012} % Date(s)
    {}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing tools to emit and validate high volumes of Mexican electronic invoices.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Cofounder - Lead developer} % Job title
    {Corporacion Augures} % Organization
    {Cd. de Mexico, Mexico} % Location
    {Nov. 2010 - May. 2012} % Date(s)
    {}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Responsible for the technical decisions concerning the development tools, databases, and deployment environments for the company applications.}
        \item {Developed a custom tool to balance investment portfolios.}
        \item {The company was adquired by our only client.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Technical Leader / Technical Specialist (Pre-sales)} % Job title
    {IDS Comercial} % Organization
    {Cd. de Mexico, Mexico} % Location
    {Dec 2009 - Feb 2011} % Date(s)
    {}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led a team of 5 developers and introduced Code Reviews and Test Driven Development methodologies improving the code quality in
        general.}
        \item {Participated in the creation of two successful sales projects analyzing and estimating the requirements.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Analyst programmer} % Job title
    {Digipro} % Organization
    {Cd. de Mexico, Mexico} % Location
    {Mar. 2008 - Nov. 2009} % Date(s)
    {}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and developed an HTML/JavaScript based document visualisation control to replace an ActiveX plugin.}
        \item {Developed a tool to bootstrap new instances of the main application for new customers reducing the configuration time of a new project
        from 4 days to 4 hours.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Intern / Software developer} % Job title
    {CIMAT} % Organization
    {Guanajuato, Mexico} % Location
    {Sep. 2007 - Feb. 2008} % Date(s)
    {}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed image and video componentes for a Digital Whiteboard Software.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
